---
title: "Twitter influence"
output: html_notebook
---

This notebook is to help me discover the path of least resistance for the Kenya's online promoters. To mean who spurs conversations and who doesn't?



```{r}
library(tidyverse)
library(stringr)
tweeps <- c("Queen_gathoni", "Brianmbunde", "Asamoh_", "Kenyanpundit",
            "LarryMadowo", "BonifaceMwangi", "bikozulu", "C_NyaKundiH",
            "ninanjira", "nanjala1","sammygichuru","VinieO","masaku_",
            "MutahiNgunyi","BobCollymore","MohajichoPevu","xtiandela",
            "JulieGichuru","KoinangeJeff","mwalimchurchill","ItsMainaKageni",
            "BahatiKenya","Mbusii","CarolineMutoko","lillian_muli",
            "RevKathyKiuna",
            "GraceMsalame","OfficialJMbugua","ADELLEO","AnneKiguta","ThisisEss",
            "AngelaAngwenyi","muthoninjoba","Edith_kimani","VickyRubadiri",
            "AnitaNderu","RobertAlai","bankelele","coldtusker","rookieke",
            "kaluhiskitchen")
tweeps_kot=c("BelAkinyii","cnyakundi_","breegathoni2","ashleyahmed19",
"StaceyKerubo","joyigamba","FarahMaalimM","CpaWaweru","KaluhisKitchen",
"Dianne_Meria","magymacha22","Midnimo254","Fahhimah","HNdonyi","ImJudyMuriithi",
"RoadAlertsKE","pyepar","teairra_natasha","sivenziakelly","lengerdedh",
"QueenOlwala","FiiDee_","xtiandela","LieDnt","MbucuWilson","vinny_wa","cyncarly_",
"Mollage_","rumaysa_jamila","Moh_Clementines","MisRoxie","JuliusYegoKE","candybaibe170",
"ResumesKenya", "Sc0fy_","TextBookCentreL","Joykwendo","ro_roseaja", "Misshekoh",
"shecycles","kenyanpeasant","torrymartins","Kimarujnr","LatiffCherono",
"Shirley_Sein", "Lyngakuru","Einterseptor","tianta_","katenderu","jmarjawar",
"ChampagneKimie","GrantBrooke","Kipezer","tabbynn","mutheumbondo","PTitia_",
"TheStarKenya","CarolRadull","nikkikalaine","an0nniemous_", "JanetMacharia",
"LamsKenya_","JoyceLorna","RailaOdinga","AnnaNjuguna","Sheilakari","MonyqueXO",
"HellenMasido","rae254rae","AnneKiguta","njiiru","mukuiyaR","Ramah_Nyang",
"Yenyewe","galladostinoes","UKenyatta","JoyDoreenBiira", "Trackmann","mckym",
"DjProtegeKenya","QueenGathoni","Yafesi_Musoke","benstake", "JICHOdaDOG",
"sluvinzu","Owaahh","IamGe","MrNyoike","shyolympia","pierrengash","iWateba",
"kuirab","Jay_Kamau","nanciemwai","bonifacemwangi","princelySid","NiNanjira",
"Kamandeh_","RamzZy_","Mehboobah","silvianjoki","Kurlycheeks","JamesMutuaEng",
"DjEyn","nishet","AKenyanG","mmnjug","smusyoka","tommakau","dailynation",
"ClanSewe","LazzLo_","paulakahumbu","coldtusker","RobertAlai","gathara","Nekesa",
"mentalacrobatic","YvonneNyamao","Dee_kui","ashikoyeO","Nanjala1","Asamoh_")

#kot <- read_html("https://twitter.com/AdiePrestone/lists/kot/members") %>%
#  html_nodes(xpath='//*[contains(concat( " ", @class, " " ), concat( " ", "u-dir", " " ))]') %>% html_text()
# install.packages("devtools")
# devtools::install_github("mkearney/rtweet")
library(rtweet)
twitter_token=create_token(app = "Adie", consumer_key="%%%%%%%%%%%%%%%%", consumer_secret="%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%", cache = TRUE)
tweeps_list <- c(tweeps,tweeps_kot)

kenyan_users <- lookup_users(tweeps_list)
# tweets_all <- NULL
# for ( i in 146:length(tweeps_list)){
# tweets_user <- get_timeline(tweeps_list[i],n=1500, token=token_here)
# tweets_all <- rbind(tweets_all,tweets_user)
# }
# 
# saveRDS(tweets_all, file="kot_tweets.RDS")
# 
# tweets_all2 <- tweets_all
# tweets_all2<- tweets_all2 %>%
#   mutate(tweet_url=paste0("https://twitter.com/",screen_name,"/status/",status_id))
# tweets_all2$type <- ifelse(grepl("RT",str_sub(tweets_all2$text,1,2))==TRUE,
#                           "retweet","own tweet")
# 
# tweets_all <- 
# 
# self_tweets <- tweets_all2 %>%
#   filter(!type %in% "retweet")
```
```{r, loading_kotlist}
# library(rvest)
# url <- "https://twitter.com/login"
# session <- html_session(url)
# form <- html_form(read_html(url))[[2]]
# 
# filled_form <- set_values(form,
#                           "session[username_or_email]" = "adieprestone",
#                           "session[password]" = "%%%%%%%%")
# 
# kot_lists <- submit_form(session, filled_form) %>%
#   jump_to("https://twitter.com/AdiePrestone/lists/kot/members") %>% 
#   html_nodes(xpath='//div/a/span/b') %>%
#   html_text()


```

next we will carry out a network analysis on the tweets to determine the most central figure on kenyan twitter

And these variables that I used for building my ‘top score’: I simply calculate a percentile for each of those variables and sum it altogether for each user. Given that each variable’s percentile will give me a value between 0 and 1, The final score can have a maximum value of 5.
```{r, top_50}
kenyan_users %>% select(dplyr::contains("count")) %>% head()

kenyan_users_ranking <- kenyan_users %>%
  distinct() %>%
  filter(protected == FALSE) %>% 
  select(screen_name, dplyr::contains("count")) %>% 
  unique() %>% 
  mutate(followers_percentile = ecdf(followers_count)(followers_count),
         friends_percentile = ecdf(friends_count)(friends_count),
         listed_percentile = ecdf(listed_count)(listed_count),
         favourites_percentile = ecdf(favourites_count)(favourites_count),
         statuses_percentile = ecdf(statuses_count)(statuses_count)
         ) %>% 
  group_by(screen_name) %>% 
  summarise(top_score = sum(followers_percentile, friends_percentile,
                            listed_percentile, favourites_percentile,
                            statuses_percentile)) %>% 
  ungroup() %>% 
  mutate(ranking = rank(-top_score))
  
top_50 <- kenyan_users_ranking %>% arrange(desc(top_score)) %>% head(50) %>% arrange(desc(top_score))
top_50 
```


```{r reading_friends}
top50_lookup <- kenyan_users %>%
  filter(screen_name %in% top_50$screen_name) %>% 
  select(screen_name, user_id)
  
friends_top50a <-   map(top_50$screen_name[1:15], get_friends)
names(friends_top50a) <- top_50$screen_name[1:15]

# 15 minutes later....
friends_top50b <- map(top_50$screen_name[16:30], get_friends)
names(friends_top50b) <- top_50$screen_name[16:30]

# 15 minutes later....
friends_top50c <- map(top_50$screen_name[31:45], get_friends)
names(friends_top50c) <- top_50$screen_name[31:45]

# 15 minutes later....
friends_top50d <- map(top_50$screen_name[46:50], get_friends)
names(friends_top50d) <- top_50$screen_name[46:50]

#appending the lists together
friends_top50_part1 <- append(friends_top50a, friends_top50b)
friends_top50_part2 <- append(friends_top50c, friends_top50d)
friends_top50 = append(friends_top50_part1, friends_top50_part2)
names(friends_top50) <- top_50$screen_name
saveRDS(friends_top50, file="friends_top50.rds")

friends_top50=readRDS("friends_top50.rds")
# purrr - trick I've been banging on about!
friends_top <- map2_df(friends_top50, names(friends_top50), ~ mutate(.x, twitter_top_user = .y)) %>% 
  rename(friend_id = user_id) %>% select(twitter_top_user, friend_id)

```
Select friends from the list

```{r final_friends}
final_friends_top50 <- friends_top  %>% 
  filter(friend_id %in% top50_lookup$user_id)

```

add friends screen name and the final product

``` {r add_screen}
# add friends' screen_name
final_friends_top50$friend_name <- top50_lookup$screen_name[match(final_friends_top50$friend_id, top50_lookup$user_id)]

final <- final_friends_top50 %>% select(-friend_id)

head(final)
```
Mapping it all out

```{r network}
extrafont::loadfonts(device="win")
library(igraph)
library(ggraph)
f1 <- graph_from_data_frame(final, directed = TRUE, vertices = NULL)
V(f1)$Popularity <- degree(f1, mode = 'in')

ggraph(f1, layout='kk') + 
  geom_edge_fan(aes(alpha = ..index..), show.legend = FALSE) +
  geom_node_point(aes(size = Popularity)) +
  theme_graph( fg_text_colour = 'black') 
  
ggraph(f1, layout='kk') + 
  geom_edge_fan(aes(alpha = ..index..), show.legend = FALSE) +
  geom_node_point(aes(size = Popularity)) +
  geom_node_text(aes(label = name, fontface='bold'), 
                 color = 'white', size = 3) +
  theme_graph(background = 'dimgray', text_colour = 'white',title_size = 30)+
  scale_edge_color_brewer(palette = 'Set1')+ 
  labs(title='Network of the Top 50 KOT users')
```
```{r top50_graphed}
ggraph(f1, layout='kk') + 
  geom_edge_fan(aes(alpha = ..index..), show.legend = FALSE) +
  geom_node_point(aes(size = Popularity)) +
  theme_graph( fg_text_colour = 'black') +
  geom_edge_link(aes(colour = "steelblue")) +
  scale_edge_color_brewer(palette = 'Set1') + 
  labs(title='Top 50 KOT users and the links between them')
```
```{r}
tweets_top50 <- tweets_all %>%
  filter(screen_name %in% top_50$screen_name)

tweets50 <- NULL
for ( i in 1:length(top_50$screen_name)){
tweets_user <- get_timeline(top_50$screen_name[i],n=1500, token=token_here)
tweets50 <- rbind(tweets50,tweets_user)
}

tweets50$type <- ifelse(grepl("RT",str_sub(tweets50$text,1,2))==TRUE,
                          "retweet","own tweet")

tweets50_left <- tweets50 %>%
  filter(!type %in% "retweet")

tweets50_sum <- tweets50_left %>%
  group_by(screen_name) %>%
  summarise(retweets=mean(retweet_count), total_retweets=sum(retweet_count),
            favorites=mean(favorite_count), total_favs=sum(favorite_count))

ggplot(data=tweets50_sum, aes(x=retweets, y=favorites))+
  geom_point()
```
```{r}
# i=1
# tweets <- rtweet::search_tweets(q = tweets50_left$screen_name[i],
#                                 sinceId = tweets50_left$status_id[i],
#                                 n = 2000, 
#                                 include_rts = FALSE)
# 
# tweets <- tweets %>%
#   distinct()
# tweet_replies <- tweets %>%
#   filter(tweets$in_reply_to_status_status_id %in% tweets50_left$status_id)
# tweets
# # for ( i in 1: length(tweets50_left$status_id)){}
# tweets_replies <- function(screen_name, ostatus_id){
#   tweets_searched=rtweet::search_tweets(q = screen_name,
#                                 sinceId = ostatus_id,
#                                 n = 2000, 
#                                 include_rts = FALSE,
#                                retryonratelimit=TRUE)
# tweets_searched = tweets_searched %>%
#   distinct() 
# replied_tweets=tweets_searched %>%
#   filter(in_reply_to_status_status_id %in% ostatus_id) %>%
#   summarise(reply_number=length(in_reply_to_status_status_id))
# return(replied_tweets$reply_number)
# }
# number_replies <- NULL
# for (k in 1:2){#length(tweets50_left$screen_name)){
# first_tweet <- tweets_replies(screen_name=tweets50_left$screen_name[k],
#                               ostatus_id=tweets50_left$status_id[k]) %>%
#   as.data.frame()
# names(first_tweet) <- "number_replying"
# number_replies <- rbind(number_replies, first_tweet)
# }
# 
# tweets50_left$replies <- lapply(tweets50_left$screen_name,
#                                        tweets50_left$status_id,tweets_replies)
# 
# 
# 
# 
# id <- tweets$status_id[5]
# diff <- 1
# while (diff != 0) {
# id_next <- tweets %>%
#   filter(in_reply_to_status_status_id %in% id) %>%
#   select(status_id) %>%
#   pull()
# id_new <- unique(c(id, id_next))
# diff <- length(id_new) - length(id)
# id <- id_new
# }
# 
# all_replies <- tweets %>% 
#   filter(in_reply_to_status_status_id %in% id)
```

```{r, reading_replies}
tweets50_left$status_link <- 
  paste0("https://twitter.com/", tweets50_left$screen_name, "/status/",
         tweets50_left$status_id)

library(rvest)
url <- "https://twitter.com/login"
session <- html_session(url)
form <- html_form(read_html(url))[[2]]

filled_form <- set_values(form,
                          "session[username_or_email]" = "%%%%%%%%%%%%%%%%",
                          "session[password]" = "%%%%%%%%%%%%%%%")
tweets50_left <- readRDS("tweets50_left.rds")
replies <- readRDS("replies39444.rds")
replies <- NULL
saveRDS(replies, file=paste0("replies",i,".rds"))
for (i in 1:length(tweets50_left$screen_name)){
reply_nums <- submit_form(session, filled_form) %>%
  jump_to(tweets50_left$status_link[i]) %>% 
  html_node(xpath='//*[contains(concat( " ", @class, " " ), concat( " ", "ProfileTweet-actionCountForPresentation", " " ))]') %>%
  html_text() %>% as.numeric() %>% as.data.frame()
replies <- rbind(replies,reply_nums)
}
names(replies) <- "number_replies"
saveRDS(tweets50_left, file="tweets50_left.rds")
tweets50_left$number_replies <- replies
tweets50_left
```




```{r,top_linked_tweeps}
usersdata <- NULL
for (i in 1:length(screen_names)){
user_total <- submit_form(session, filled_form) %>%
  jump_to(paste0("https://twitter.com/",screen_names[i])) %>% 
  html_nodes(xpath='//*[contains(concat( " ", @class, " " ), concat( " ", "ProfileNav-value", " " ))]') %>%
  html_text() %>% as.character()
user_data = gsub("K","000",
                   gsub("M","000000",
                        gsub("\\.","",
                             gsub(",","",
                                  gsub("\n ","",user_total[1:6]))))) %>%
  trimws(which="both") %>% as.numeric() %>% t()%>% as.data.frame() 
names(user_data) = c("tweets","following","followers","likes","lists","moments")
user_data$screen_name=screen_names[i]
usersdata <- rbind(usersdata,user_data)
}
users_popularity=data.frame(
  screen_name=c("xtiandela", "C_NyaKundiH", "KoinangeJeff", "paulakahumbu", 
         "kenyanpundit", "ADELLEO", "Asamoh_", "RobertAlai", "CarolRadull",
         "JulieGichuru", "RamzZy_", "pyepar",  "LarryMadowo", "Brianmbunde",
         "JoyDoreenBiira", "NiNanjira", "ChampagneKimie", "lillian_muli", 
         "CpaWaweru", "smusyoka", "gathara", "RoadAlertsKE", "ItsMainaKageni",
         "benstake", "Kipezer", "vinny_wa", "VickyRubadiri", "CarolineMutoko", 
         "TheStarKenya", "bonifacemwangi", "MwalimChurchill", "AnneKiguta", 
         "coldtusker", "mmnjug", "GraceMsalame", "Trackmann", "Nanjala1",
         "Owaahh", "RookieKE", "mentalacrobatic", "bankelele", "Mbusii", 
         "dailynation", "KaluhisKitchen", "masaku_", "mckym", "iWateba", 
         "Sheilakari", "QueenGathoni", "JICHOdaDOG"),
  top50_popularity=c(5,2,3,7,5,4,1,3,8,4,3,2,5,5,7,4,3,7,1,6,6,2,7,4,3,3,4,8,7,
                     7,5,5,3,5,6,3,1,6,1,3,3,2,5,3,4,2,2,2,2,2)
  )
users_popularity$screen_name=as.character(users_popularity$screen_name)

tweets50_replies <- tweets50_left %>%
  group_by(screen_name) %>%
  summarise(tweets=length(user_id),
            retweets=sum(retweet_count),
            favorites=sum(favorite_count),
            replies_all=sum(na.omit(number_replies))) %>%
  arrange(desc(replies_all))
tweets50_all <- left_join(tweets50_replies, users_popularity, by="screen_name")
top50_ranked=tweets50_all %>%
#   filter(screen_name %in% c("GraceMsalame","Trackmann","kenyanpundit",
#          "smusyoka","CarolRadull","gathara","Ramzzy_",
#          "Brianmbunde","ADELLEO","Owaahh","KaluhisKitchen")) %>%
  group_by(screen_name, top50_popularity) %>%
  summarise(influence=retweets/tweets,
         engagement=replies_all/tweets,
           influence_engagement=retweets/replies_all) %>%
  arrange(desc(influence_engagement)) 

library(ggrepel)
ggplot(data=top50_ranked, aes(x=top50_popularity, y= influence_engagement,
                              label=screen_name))+ geom_point(stat="identity")+
  geom_smooth() + geom_text_repel(aes(label=screen_name))+ ggthemes::theme_economist()+ggtitle("The popularity of top 50 KOT against their influence_engagement ratio")+xlab("Number of followers from top 50 KOT")
```

```{r tweet_tree}
ramzzy_tweets <- tweets50_left %>%
  filter(screen_name %in% c("RamzZy_")) %>%
  arrange(desc(number_replies))


tweets_searched=rtweet::search_tweets(q = ramzzy_tweets$screen_name[3],
                                sinceId = ramzzy_tweets$status_id[3],
                                n = 2000,
                                include_rts = FALSE,
                               retryonratelimit=TRUE)
tweets_searched = tweets_searched %>%
  distinct()
replied_tweets=tweets_searched %>%
  filter(in_reply_to_status_status_id %in% ramzzy_tweets$status_id[3])


id <- replied_tweets$status_id[5]
diff <- 1
while (diff != 0) {
id_next <- tweets %>%
  filter(in_reply_to_status_status_id %in% id) %>%
  select(status_id) %>%
  pull()
id_new <- unique(c(id, id_next))
diff <- length(id_new) - length(id)
id <- id_new
}

```
